Characterization of gaps in directly bonded Si compound optics

### 2014-03-04 AO_bondedSi.tex
Make power law dust distribution discussion more quantitative

The foundation paper on Si bonding came in 1986\cite{1986JAP....60.2987S}.  After that, there was a sequence of papers using IR imaging to look for evidence of defects in the bond.  In some of cases, the bond propagation could be directly monitored\cite{1988JaJAP..27L2364S, 1995ApPhL..67.3614G}.  The bond process could be shown to be bubble-free\cite{1988JaJAP..27L2364S, 1989JaJAP..28L2141L}.  The bond surface energy was directly measured\cite{1989JaJAP..28L2141L}.  The causes and remedies for bubble formation were discussed as early as 1990\cite{Mitani1990}.  Specifically, the IR bubble density changes as a function of anneal temprature\cite{1992JEMat..21..669M}, with bubbles disappearing at temperatures greater than 1100$^\circ$ C.  The chemistry of the bonding interface began to be understood with infrared absorption spectroscopy and multiple internal reflection spectroscopy\cite{feijoo1994}, which lent credibility to the idea of distinct temperature phases and evidence for Si$-$H bonds\cite{1995ApPhA..61..101R}.  A robust picture of the chemistry as a function of anneal temperature was ultimate fleshed out\cite{1996JaJAP..35.2102R, 1998AnRMS..28..215G}.  Other variables potentially affecting bond strength were studied, for example surface roughness\cite{JJAP.37.4197}, surface topography \cite{2001JOptA...3...85G}, surface preparation \cite{1996ApPhL..68.2222T}, annealing time \cite{2000JAP....88.4404H}, ambient pressure and substrate thickness \cite{1995ApPhL..67..863G, 2007ApOpt..46.6793H}, moisture and defects \cite{2001JAP....89.6013L}.  No where in the literature did we find a technique similar to the one presented here, probably because the technique relies on the high precision of relatively new IR capable spectroscopy that wasn't widely available until this decade.

@@

Consider the following two conceivable pitfalls in Si direct bonding.  First, particles at the tens of nanometer size scale are trapped between the Si pucks during bonding.  This potential problem is especially acute for silicon direct bonding compared to bonding of popular low-index optical materials.  A typical particle surface flux is shown in Figure 5 of Cooper 1986\cite{Cooper_1986}.  The flux of particles is a step function of particle size.  For every micron sized particle causing Newton's rings, there will be as many as 100,000 more ten-nanometer sized particles.

The second pitfall to consider is that the stiff non-flat Si surfaces will not conform upon contact leaving the complement of the aberrations as an air gap. Similarly, surface roughness will also limit the bonding strength  \cite{JJAP.37.4197,2001JOptA...3...85G}.  The details of this aspect of the bonding process are outside the scope of this paper.

>>>>

The foundation paper on Si bonding came in 1986\cite{1986JAP....60.2987S}.  After that, there was a sequence of papers using IR imaging to look for evidence of defects in the bond.  In some of cases, the bond propagation could be directly monitored\cite{1988JaJAP..27L2364S, 1995ApPhL..67.3614G}.  The bond process could be shown to be bubble-free\cite{1988JaJAP..27L2364S, 1989JaJAP..28L2141L}.  The bond surface energy was directly measured\cite{1989JaJAP..28L2141L}.  The causes and remedies for bubble formation were discussed as early as 1990\cite{Mitani1990}.  Specifically, the IR bubble density changes as a function of anneal temprature\cite{1992JEMat..21..669M}, with bubbles disappearing at temperatures greater than 1100$^\circ$ C.  The chemistry of the bonding interface began to be understood with infrared absorption spectroscopy and multiple internal reflection spectroscopy\cite{feijoo1994}, which lent credibility to the idea of distinct temperature phases and evidence for Si$-$H bonds\cite{1995ApPhA..61..101R}.  A robust picture of the chemistry as a function of anneal temperature was ultimate fleshed out\cite{1996JaJAP..35.2102R, 1998AnRMS..28..215G}.  Other variables potentially affecting bond strength were studied, for example surface roughness\cite{JJAP.37.4197}, surface topography \cite{2001JOptA...3...85G}, surface preparation\cite{1996ApPhL..68.2222T}, annealing time \cite{2000JAP....88.4404H}, ambient pressure and substrate thickness \cite{1995ApPhL..67..863G, 2007ApOpt..46.6793H}, and moisture and defects \cite{2001JAP....89.6013L}.  No where in the literature did we find a technique similar to the one presented here, probably because the technique relies on the high precision of relatively new IR capable spectroscopy that wasn't widely available until this decade.

\section{Conceivable pitfalls in Si-Si direct bonding}

\subsection{Particles}
Consider the following two conceivable pitfalls in Si-Si direct bonding.  The obvious pitfall is particle contamination.  A single 0.6 $\mu$m particle can create a dark IR bubble from interference.  In the next section we show that smaller bubbles can unacceptably degrade the performance to as low as 10 nm.  In a class 100 cleanroom, the volume density could be as high as $\rho=100$ particles/ft$^3$, with sizes larger than 0.5 $\mu$m.  What we care about is not the volume number density of particles, but the delivered surface flux $F=\rho(D) v(D)$, where v(D) is the average freefall speed of particles, which is a function of particle size.  Figure 5 of Cooper 1986\cite{doi:10.1080/02786828608959094} shows the surface flux (particles cm$-2$ s$-1$) vs. particle size ($\mu$m).  For a change from 1 $\mu$m to 10$-2$ $\mu$m, there is an increase in a factor of $10^4$ in the particle flux expected.  In other words:
$$\log(F) = -2\log(D) + const.$$

So there will be roughly $10^4$ times more 10 nm sized particles than 1 $\mu$m sized particles, which means for every detectable IR bubble, there are thousands more particles that could unacceptably degrade the transmission performance.

\subsection{Surface roughness or aberrations}
The second pitfall to consider is that the stiff non-flat Si surfaces will not conform upon contact leaving the complement of the aberrations as an air gap. Similarly, surface roughness will also limit the bonding strength  \cite{JJAP.37.4197,2001JOptA...3...85G}.  The details of this aspect of the bonding process are outside the scope of this paper.

@@
